---
title: "challenge_problems"
output:
  html_document:
    df_print: paged
date: "2023-10-11"
---

##### A company sells LED bulbs in packages of 20 for 25$. From past records it knows that a bulb will be defective with probability 0.01. The comapany gives full refund if a customer finds more than 1 defective bulb in a pack. If company sells 100 packs how much should it expect to refund?
```{r}
#Binomial random variable
n=20
p=0.01
#Probability of getting more than 1 defective bulb in a package = P(X>=2) or 1-P(X<2)
p_new=1-pbinom(1,n,p)
p_new
```
```{r}
n=100#Total number of packages
p=p_new#Probability of getting defective package=p_new
#Expected value=n*p
#Expected refund=25*n*p
25*n*p

```


##### During assembly a product is equipped with 5 control switches each of which has probability of 0.04 being defective. What is the probability that 2 defective switches encountered before 5 non defective?
```{r}
#Negative Binomial random variable
p=0.04#Probability of getting a defective switch
r=2
#It would take total 7 trials to find 2 defective switches before 5 non-defective switches.
j=7
dnbinom(j-r,r,p)

```
#### Suppose that class of 50 students appear for a test and 41 out of 50 passed the test while the remaining 9 students have failed the test. Find the probability that in a group of 10 students selected at random none of them have failed the test and atleast 3 students have failed the test
```{r}
#Hyper geometry 
nsuccess=9
nfailures=41
n=10
#None have failed the test = P(X=0)
dhyper(0,nsuccess,nfailures,n)
#At least 3 students have failed the test = P(X>=3) or 1-P(X<3)
#dhyper(3,nsuccess,nfailures,n)+dhyper(4,nsuccess,nfailures,n)+dhyper(5,nsuccess,nfailures,n)+dhyper(6,nsuccess,nfailures,n)+dhyper(7,nsucce#ss,nfailures,n)+dhyper(8,nsuccess,nfailures,n)+dhyper(9,nsuccess,nfailures,n)+dhyper(10,nsuccess,nfailures,n)
1-sum(dhyper(c(0:2),nsuccess,nfailures,n))
```
```{r}
#Poisson random variable
n=1e6
p=1e-6
j=5
dbinom(j,n,p)
dpois(5,1)
```

