---
title: "Dishwasher Problem"
output:
  pdf_document: default
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---

#### Sampling space is the 5 dishwashers. The event of atleast 4 dishes out of getting broken by the same dishwasher is equally likely.

```{r}
s=c('d1','d2','d3','d4','d5')
p=replicate(5,1/5)
S=sample(s,5,replace=TRUE,prob=p)
print(S)
```

#### Replicating the simulations for 100000 iterations

```{r}
simTrial=function(){
 S=sample(s,5,replace=TRUE,prob=p)
  return(S)
}
nsimulations=100000
simulatedData=replicate(nsimulations,simTrial())
#print(simulatedData)
```

```{r}
print(simulatedData)
```

#### Consider d1 is the dishwasher breaking atleast 4 out 5 dishes. So we need to check the fraction of d1 appearing 4 or more than 4 times.

```{r}
checkEvent=function(data){
  if(sum(data=='d1')>=4)
    return(1)
  else
    return(0)
}
```

```{r}
print(mean(apply(simulatedData,2,checkEvent)))
```

#### Based on the probability value, the probability of one dishwasher breaking atleast 4 out of 5 is relatively low. So the hypotheses of the particular dishwasher being "not clumsy" is wrong.

```{r}
(choose(5,4)*choose(4,1)+1)/(5^5)
```
